Comparing R packages for calculation of persistent homology

### 2019-12-16 tdabench-paper/tdabench.Rmd
Updated paper title/authors

---
title: Comparing efficiency of R packages implementing calculation of persistent homology
author:
  - name: Author One
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author1@work
  - name: Author Two
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author2@work
abstract: >
  An abstract of less than 150 words.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).
\bibliography{RJreferences}

>>>>

---
title: Comparing R packages for calculation of persistent homology
author:
  - name: Eashwar V. Somasundaram
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author1@work
  - name: Shael E. Brown
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author2@work
  - name: Adam Litzler
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author1@work
  - name: Raoul R. Wadhwa
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author1@work
  - name: Jacob G. Scott
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author1@work
abstract: >
  An abstract of less than 150 words.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).
\bibliography{tdabench-paper}
